### 2010-06-14 code/subarchitectures/visualization.sa/trunk/doc/v11n.tex
v11n: docs

The library provides a client component that interacts with the server. The
client is devised in such a way that its use is as trivial as the use of
OpenCV's function cvShowImage(). For simple objects the server can also
be used without a client if the developer is willing to use the file system
as a communication channel. This involves a CAST component that monitors
the file system and sends the newly created files to the server.

First we will show how to use the file system monitor and then we will give
instructions for the use of the real client.

>>>>

The C++ client library provides a client interface that enables the interaction
with the server. It lets the programmer send objects to be dispayed to the
server and receive notifications about the events emited by the user interface
that was built on the server by the client component.
\todo{TODO: add interfaces for Java and Python}

For simple objects the server can be used without linking to the display client
because the file system as a communication channel. To do this a CAST
component FileMonitor has to be added to the cast file and configured to
monitor certain files that are created by other componetns.
